---
title: "ResPECT central analysis verification"
author: "Alexandria C. Brown"
date: "August 23, 2017"
output: html_document
---

```{r setup}
library("mice")
library("lme4")
library("lattice")
library("gridExtra")
library("MASS")
library("dplyr")
load("/home/lex/Desktop/ARMS-models-workspace.rda")

ls()  #items in the workspace
```

##Primary outcome, ITT and PP imputations

Each will be examined for the per protocol (PP) and intention to treat (ITT) analyses.

```{r}
summary(demog$Influenza) # the raw data
summary(demimp$imp$Influenza) # the imputed outcomes
get_ratio <- function(a_logical_vec){as.numeric(table(a_logical_vec)["TRUE"])/length(a_logical_vec)}
  #a ratio of positive Influenza detections divided by the total number of participants

get_ratio(demog$Influenza) # the ratio of affected participants
hist(as.numeric(apply(demimp$imp$Influenza, 2, get_ratio)), 
     round(digits=10)) # histogram showing spread of ratio in ITT imputations
densityplot(demimp, ~Influenza) # blue line is the raw data, red is ITT imputed

hist(as.numeric(apply(per_protocol_demimp$imp$Influenza, 2, get_ratio)), 
     round(digits=10)) # histogram showing spread of ratio in PP imputations
densityplot(per_protocol_demimp, ~Influenza) # blue line is the raw data, red is PP imputed
```

##Secondary outcomes

The following function tests each set of imputed data as follows:
1. A qq-plot
2. Checks that the number of missing values equals the number of imputed values
3. Checks that the means of the imputed values are within one standard deviation from the mean of the real data
4. Checks that imputed values are within the range of the real data
5. Checks that imputed datasets have fewer unique values than the data

Each will be examined for the per protocol (PP) and intention to treat (ITT) analyses.

```{r}

check_imputations <- function(imputed_data_object, real_dataset_column){
  holder <- list()
qqplot(imputed_data_object[[3]], sample(real_dataset_column, 
                                          size=nrow(imputed_data_object), replace=F))
qqline(sample(real_dataset_column, size=nrow(imputed_data_object), replace=F))
##are all missing values accounted for?
holder[[1]] <- ifelse(nrow(imputed_data_object)==length(real_dataset_column[is.na(real_dataset_column)]), 
       "ALL NAs IMPUTED", "STOP! NA VALUES STILL PRESENT")
#raw data mean and sd
upper <- mean(real_dataset_column, na.rm=T)+sd(real_dataset_column, na.rm=T)
lower <- mean(real_dataset_column, na.rm=T)-sd(real_dataset_column, na.rm=T)
# are means of the imputed outcomes within 1 SD of the real data?
holder[[2]] <- ifelse(apply(imputed_data_object, 2, mean)<upper & 
         apply(imputed_data_object, 2, mean)>lower, "MEAN TEST OK", 
       "WARNING: MEAN OUTSIDE 1 SD")
##are imputed values within the range of the real data?
holder[[3]] <- ifelse(max(real_dataset_column)>=apply(imputed_data_object, 2, max) & 
         min(real_dataset_column)<=apply(imputed_data_object, 2, min), 
       "RANGE TEST OK", "WARNING: RANGE CHECK FAIL")
##imputed datasets should not have more unique values than the data
#the following function will test this
holder[[4]] <- apply(imputed_data_object, 2, 
      function(x){ifelse(length(x[!x %in% unique(x[duplicated(x)==TRUE])])<=ceiling(length(real_dataset_column[!real_dataset_column %in% unique(real_dataset_column[duplicated(real_dataset_column)==TRUE])])*0.1), 
                         "UNIQUE VALUE CHECK PASSED", "WARNING: CHECK UNIQUE VALUES")}) 
return(holder)
}

```

For each secondary outcome, there is a density plot in which imputation density is in red, while the real data density is the blue line.  Then the results of the check_imputations function is shown.

ARI, ITT

```{r}
densityplot(demimp, ~ARI_events)
check_imputations(demimp$imp$ARI_events, demog$ARI_events)
```

ARI, PP

```{r}
densityplot(per_protocol_demimp, ~ARI_events)
check_imputations(per_protocol_demimp$imp$ARI_events, demog$ARI_events)
```

LCRI, ITT

```{r}
densityplot(demimp, ~LCRI_events)
check_imputations(demimp$imp$LCRI_events, demog$LCRI_events)
```

LCRI, PP

```{r}
densityplot(per_protocol_demimp, ~LCRI_events)
check_imputations(per_protocol_demimp$imp$LCRI_events, demog$LCRI_events)
```

LDI, ITT

```{r}
densityplot(demimp, ~LDI_events)
check_imputations(demimp$imp$LDI_events, demog$LDI_events)
```

LDI, PP

```{r}
densityplot(per_protocol_demimp, ~LDI_events)
check_imputations(per_protocol_demimp$imp$LDI_events, demog$LDI_events)
```

ILI, ITT

```{r}
densityplot(demimp, ~ILI_events)
check_imputations(demimp$imp$ILI_events, demog$ILI_events)
```

ILI, PP

```{r}
densityplot(per_protocol_demimp, ~ILI_events)
check_imputations(per_protocol_demimp$imp$ILI_events, demog$ILI_events)
```

##Imputation of covariates

The covariates include 
1. The percent of times a participant reported having been in contact with someone with URI symptoms
2. Whether they were vaccinated for the flu
3. Number of children in the home under 5 years old
4. Race
5. Assigned occupational risk
6. Self-reported FPE compliance response occuring most often per participant
7. Self-reported hand hygiene compliance response occuring most often per participant
8. Age
9. Whether or not a participant reported smoking tobacco

Each will be examined for the per protocol (PP) and intention to treat (ITT) analyses.

URI_exposure_perc, ITT

```{r}
densityplot(demimp, ~URI_exposure_perc)
check_imputations(demimp$imp$URI_exposure_perc, demog$URI_exposure_perc)
```

URI_exposure_perc, PP

```{r}
densityplot(per_protocol_demimp, ~URI_exposure_perc)
check_imputations(per_protocol_demimp$imp$URI_exposure_perc, demog$URI_exposure_perc)
```

vaccine_recieved, ITT

```{r}
densityplot(demimp, ~vaccine_recieved)
check_imputations(demimp$imp$vaccine_recieved, demog$vaccine_recieved)
```

vaccine_recieved, PP

```{r}
densityplot(per_protocol_demimp, ~vaccine_recieved)
check_imputations(per_protocol_demimp$imp$vaccine_recieved, demog$vaccine_recieved)
```

num_hhmem_0_5, ITT

```{r}
densityplot(demimp, ~num_hhmem_0_5)
check_imputations(demimp$imp$num_hhmem_0_5, demog$num_hhmem_0_5)
```

num_hhmem_0_5, PP

```{r}
densityplot(per_protocol_demimp, ~num_hhmem_0_5)
check_imputations(per_protocol_demimp$imp$num_hhmem_0_5, demog$num_hhmem_0_5)
```

race, ITT

```{r}
densityplot(demimp, ~race)
check_imputations(demimp$imp$race, demog$race)
```

race, PP

```{r}
densityplot(per_protocol_demimp, ~race)
check_imputations(per_protocol_demimp$imp$race, demog$race)
```

occupational_risk, ITT

```{r}
densityplot(demimp, ~occupational_risk)
check_imputations(demimp$imp$occupational_risk, demog$occupational_risk)
```

occupational_risk, PP

```{r}
densityplot(per_protocol_demimp, ~occupational_risk)
check_imputations(per_protocol_demimp$imp$occupational_risk, demog$occupational_risk)
```

mode_fpe_freq, ITT

```{r}
densityplot(demimp, ~mode_fpe_freq)
check_imputations(demimp$imp$mode_fpe_freq, demog$mode_fpe_freq)
```

mode_fpe_freq, PP

```{r}
densityplot(per_protocol_demimp, ~mode_fpe_freq)
check_imputations(per_protocol_demimp$imp$mode_fpe_freq, demog$mode_fpe_freq)
```

mode_hand_hyg, ITT

```{r}
densityplot(demimp, ~mode_hand_hyg)
check_imputations(demimp$imp$mode_hand_hyg, demog$mode_hand_hyg)
```

mode_hand_hyg, PP

```{r}
densityplot(per_protocol_demimp, ~mode_hand_hyg)
check_imputations(per_protocol_demimp$imp$mode_hand_hyg, demog$mode_hand_hyg)
```

age, ITT

```{r}
densityplot(demimp, ~age)
check_imputations(demimp$imp$age, demog$age)
```

age, PP

```{r}
densityplot(per_protocol_demimp, ~age)
check_imputations(per_protocol_demimp$imp$age, demog$age)
```

smoke_tobacco, ITT

```{r}
densityplot(demimp, ~smoke_tobacco)
check_imputations(demimp$imp$smoke_tobacco, demog$smoke_tobacco)
```

smoke_tobacco, PP

```{r}
densityplot(per_protocol_demimp, ~smoke_tobacco)
check_imputations(per_protocol_demimp$imp$smoke_tobacco, demog$smoke_tobacco)
```


